SubsidyExplorer - Step 6: Run Model

### 2020-09-02 scripts/06_run_model.Rmd
sensitivity analysis

```{r}
# Load vessel list
pro_rate_subsidies <- F

vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)

### Not applicable currently - old experimentation with pro-rating the dollar value of different subsidies
# if(pro_rate_subsidies == T){
# 
#   vessel_dat <- vessel_dat %>%
#     mutate(B1_subs = B1_subs * 0.54, # boat construction/renovation - matched to payments based on vessels
#            B2_subs = B2_subs * 1, # fishery development projects/support services - matched to payments based on variable use
#            B3_subs = B3_subs * 0.87, # port construction and renovation - matched to payments based on vessels
#            B4_subs = B4_subs * 0.87, # price/marketing support, processing infrastructure - matched to payments based on output
#            B5_subs = B5_subs * 0.76, # non-fuel tax exemptions - matched to payments based on fishers income
#            B6_subs = B6_subs * 0.56, # foreign access agreements - matched to payments based on fishers own capital
#            B7_subs = B7_subs * 0.84, # fuel - matched to payments based on fuel use
#            bad_subs = (B1_subs + B2_subs + B3_subs + B4_subs + B5_subs + B6_subs + B7_subs))
# 
# }

vessel_dat <- vessel_dat %>%
  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
                                 TRUE ~ as.character(eez_id)))

>>>>

```{r}
# Load vessel list
vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)

# Create high seas code
vessel_dat <- vessel_dat %>%
  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
                                 TRUE ~ as.character(eez_id)))
